Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-19 manuscript/manuscript.Rmd
...

Rewards were defined to be a compound of two contributions.
The first is economical: if at time $t$ a harvest of $h_t$ is secured, then the agents total reward is increased by $h_t$.
The second regards sustainability: if an extinction happens at time step $t$, then a penalty of $-50/t$ is incurred by the agent.
The choice of the constant $50$ in this rule was rather arbitrary: we set it to be a fourth of the maximal episode length ($200$ time steps), so as to encourage the agent to find policies that do not lead to extinctions below the time scale of around 100 time steps.
\textbf{Too long of a ‘‘sorry’’ message?}

@@

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than both MSY and TAC.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, ‘‘reset’’ itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing the harvest effort and state times series obtained from these policies.

@@

The title of this piece references a mathematical biology workshop at NIMBioS
organized by Paul Armsworth, Alan Hastings, Megan Donahue, and Carl Towes in
2011 that first posed the question addressed here.

>>>>

Rewards were defined to be a compound of two contributions.
The first is economical: if at time $t$ a harvest of $h_t$ is secured, then the agents total reward is increased by $h_t$.
The second regards sustainability: if an extinction happens at time step $t$, then a penalty of $-50/t$ is incurred by the agent.
The choice of the constant $50$ in this rule was rather arbitrary: we set it to be a fourth of the maximal episode length ($200$ time steps), so as to encourage the agent to find policies that do not lead to extinctions below the time scale of around 100 time steps.
\textbf{Too long of a "sorry" message?}

@@

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than both MSY and TAC.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, "reset" itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing the harvest effort and state times series obtained from these policies.

@@

The title of this piece references a mathematical biology workshop at NIMBioS
organized by Paul Armsworth, Alan Hastings, Megan Donahue, and Carl Towes in
2011 seeking to pivot control from 'optimal' to 'pretty darn good'.
